Meet the team

### 2025-05-14 index.qmd
updates to multiple pages

@@

<font color="#d08770">[March 03 2025].</font> **New Preprint**. Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, J.G.A., & Carter, M.J. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. [https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}

>>>>

<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, & Cashaback JGA. (Accepted). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*.

@@

<font color="#d08770">[March 03 2025].</font> **New Preprint**. Lalli M, Al Afif N, Tang J, Hasan H, Dissanayake E, Sussman V, Lokesh R, Rathwell S, Cashaback JGA, & Carter MJ. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. [https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}

### 2025-05-14 papers.qmd
minor updates
render site
updates to multiple pages

---
title: "Papers"
pagetitle: "CarterLab | Papers"
toc: true
toc-title: "Jump to..."
---

@@

@@

- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ. (2023). The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}

>>>>

---
title: ""
pagetitle: "CarterLab | Papers"
toc: true
toc-title: "Jump to..."
---

@@

- Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, JGA., & Carter, MJ. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. --- [{{< ai doi >}}](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank" style="color: inherit;"}

@@

- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ. The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}

### 2025-05-14 teaching.qmd
updates to multiple pages

---
title: "Teaching"
pagetitle: "CarterLab | Teaching"
toc: false
---

Updates in progress...

>>>>

---
title: ""
pagetitle: "CarterLab | Teaching"
toc: false
---

```{r}
#| echo: false

library(markdown)
library(tinytable)

tibble::tibble(
    `FALL 2025` = c(
        "Motor Control and Learning (KINESIOL 2MC3)...*Coming soon*",
        "Neurorehabilitation and Robotics (KINESIOL 4TT3)...*Coming soon*",
        "Scientific Computing for Reproducible Science (KINESIOL 736)...*Coming soon*"
        )
) |> 
    tt(width = 1) |> 
    group_tt(i = list(
        "Undergraduate courses" = 1,
        "Graduate courses" = 3
    )) |> 
    format_tt(j = 1, markdown = TRUE) |> 
    style_tt(i = 0, background = "#0077bb", color = "white") |> 
    style_tt(i = c(1,4), background = "#eceff4", bold = TRUE)
```

### 2025-05-14 team.qmd
updates to multiple pages

<div class="team-member">
  <img src="images/daniel-deletsu.jpg" alt="images/daniel-deletsu.jpg" class="team-img">
  <div class="team-info">
  <h4> Daniel Deletsu, B.Sc. </h4>
  <p> M.Sc. Student </p>
  <p> deletsud [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Andrea Albert Pravin </h4>
  <p> Undergraduate thesis student </p>
  <p> BIOLOGY 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Faris Almoni </h4>
  <p> Undergraduate practicum student </p>
  <p> LIFESCI 4A03 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Gaile Cheng </h4>
  <p> Undergraduate practicum student </p>
  <p> SCIENCE 2RP3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/michael-croteau.jpg" alt="images/michael-croteau.jpg" class="team-img">
  <div class="team-info">
  <h4> Michael Croteau </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L12 A/B </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Enuri Dissanayake </h4>
  <p> Undergraduate thesis student </p>
  <p> LIFESCI 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Leo Ducharme </h4>
  <p> Undergraduate thesis student </p>
  <p> PNB 4D06 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/tara-esbati.jpg" alt="images/tara-esbati.jpg" class="team-img">
  <div class="team-info">
  <h4> Tara Esbati </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Shiuli Khanna </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L12 A/B </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Linsea Martin </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/courtney-nguyen.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Courtney Nguyen </h4>
  <p> Undergraduate thesis student </p>
  <p> HTHSCI 4A15 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/shiv-peshwa.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Shiv Peshwa </h4>
  <p> Undergraduate practicum student </p>
  <p> KINESIOL 3RP3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Dana Rugole </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Biochemistry) </p>
  </div>
</div>

<div class="team-member">
  <img src="images/nicole-su.jpg" alt="images/nicole-su.jpg" class="team-img">
  <div class="team-info">
  <h4> Nicole Su </h4>
  <p> Undergraduate thesis student </p>
  <p> BIOLOGY 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/vida-sussman.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Vida Sussman </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/eshaa-tariq.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Eshaa Tariq </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Kinesiology) </p>
  </div>
</div>

<div class="team-member">
  <img src="images/eleanore-wu.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Eleanore Wu </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Kinesiology) </p>
  </div>
</div>

<div class="team-member">
  <img src="images/jacqueline-zheng.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Jacqueline Zheng </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L09 </p>
  </div>
</div>

@@

Lidia Barbera (2023-24); Hibaa Hasan (2023-24); Ola Schwarzenberg (2023-24); Mithun Manivannan (2023-24); Chitrini Tandon (2021-23); Alyssa Skouros (2022-23); Kiana Masoudi (2022-23); Raika Bourmand (2021-22); Armin Sariaslani (2021-22); Katharine (Katie) Douglas (2021-22); Thinzar Soe (2021-22); Julianna Marfisi (2020-21); Matthew Tobis (2020-21); Andrew Poskus (2020-21); Sherry Feldman (2019-20); Olena Leshchyshen (2019-20); Noura Balbaa (2019-20)

@@

Aashna Gujral (2024); Dami Alabi Benson (2024); Michael Croteau (2024); Francesca Caputo (2024); Jil Soni (2024); Navishka Brahmbhatt (2024); Aditya Trivedi (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)

@@

Vida Sussman (2022-24); Elizabeth Mitchell (2020-23); Celeste de Faveri (2021-23); Lidia Barbera (2022-23); Hibaa Hasan (2022-23); Faith Adams (2022); Chitrini Tandon (2021-22); Kristen Arnold (2021-22); Alison Williams (2018-20); Andrew Poskus (2019); Kevin Gilotra (2019); Ashton Yuen (2019); Mackenzie (Kenzie) Bell (2019-21); Olena Leshchyshen (2018-19); Yu (Sarah) Fu (2018-19)

>>>>

<div class="team-member">
  <img src="images/daniel-deletsu.jpg" alt="images/daniel-deletsu.jpg" class="team-img">
  <div class="team-info">
  <h4> Daniel Deletsu, B.Sc. </h4>
  <p> M.Sc. Candidate </p>
  <p> deletsud [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/michael-croteau.jpg" alt="images/michael-croteau.jpg" class="team-img">
  <div class="team-info">
  <h4> Michael Croteau </h4>
  <p> M.Sc. Student </p>
  <p> croteaum [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Maria Alex </h4>
  <p> Undergraduate Research Assistant </p>
  <p> McMaster Institute for Research on Aging 2025 Summer Research Fellowship Winner </p>
  </div>
</div>

@@

Shiuli Khanna (2024-25); Michael Croteau (2024-25); Enuri Dissanayake (2024-25); Nicole Su (2024-25); Courtney Nguyen (2024-25); Leo Ducharm (2024-25); Andrea Albert Pravin (2024-25); Jacqueline Zhang (2024-25); Lidia Barbera (2023-24); Hibaa Hasan (2023-24); Ola Schwarzenberg (2023-24); Mithun Manivannan (2023-24); Chitrini Tandon (2021-23); Alyssa Skouros (2022-23); Kiana Masoudi (2022-23); Raika Bourmand (2021-22); Armin Sariaslani (2021-22); Katharine (Katie) Douglas (2021-22); Thinzar Soe (2021-22); Julianna Marfisi (2020-21); Matthew Tobis (2020-21); Andrew Poskus (2020-21); Sherry Feldman (2019-20); Olena Leshchyshen (2019-20); Noura Balbaa (2019-20)

@@

Vida Sussman (2024-25); Tara Esbati (2024-25); Shiv Peshwa (2025); Linsea Martin (2024-25); Faris Almoni (2025); Gaile Cheng (2025); Aashna Gujral (2024); Dami Alabi Benson (2024); Michael Croteau (2024); Francesca Caputo (2024); Jil Soni (2024); Navishka Brahmbhatt (2024); Aditya Trivedi (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)

@@

Eshaa Tariq (2024-25); Eleanore Wu (2024-25); Shiv Peshwa (2024); Dana Rugole (2025); Vida Sussman (2022-24); Elizabeth Mitchell (2020-23); Celeste de Faveri (2021-23); Lidia Barbera (2022-23); Hibaa Hasan (2022-23); Faith Adams (2022); Chitrini Tandon (2021-22); Kristen Arnold (2021-22); Alison Williams (2018-20); Andrew Poskus (2019); Kevin Gilotra (2019); Ashton Yuen (2019); Mackenzie (Kenzie) Bell (2019-21); Olena Leshchyshen (2018-19); Yu (Sarah) Fu (2018-19)
